Fourmile Calibrations

### 2023-03-07 calibration_output.Rmd
some updates

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)

@@

# plot time series of LAI over for HRU 12
hru_select %>%
  mutate(year = year(time)) %>% 
  filter(value == 12) %>% 
ggplot(aes(x = time)) +
  geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) +
  geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) +
  ggtitle('LAI over time for HRU 12 (unburned)') +
  scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange', 
                                            "HRU12_unburn_statn"='springgreen4')) +
  theme_bw()

@@

```{r reach hydrographs, echo = F}

# reach <- read_csv('reach_all.csv') %>%
#   mutate(reach = as.factor(reach)) %>%
#   pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')
# 
#   
# plotq_reach <- function(reach_name) {
#   {reach %>%
#     filter(reach == reach_name) %>%
#     ggplot(aes(x = date,
#                y = q_cms,
#                color = cal)) + 
#     geom_line() + 
#     ggtitle(reach_name) +
#     theme_bw()} %>%
#     ggplotly()
#   
# }
# 
# name <- levels(reach$reach)
# 
# try2 <- lapply(name, plotq_reach)
# 
# htmltools::tagList(try2)
# 
# ```
# 
# ### Overall KGE by reach
# 
# ```{r reach kge, echo = F}
# 
# reach_pivot <- reach %>%
#   pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
#   mutate(WY = as.factor(calcWaterYear(date)))
# 
# reach_kge_all <- reach_pivot %>%
#   group_by(reach) %>%
#   summarize(grid2011 = KGE(grid_2011, obs),
#             grid2012 = KGE(grid_2012, obs),
#             grid2013 = KGE(grid_2013, obs),
#             grid2014 = KGE(grid_2014, obs),
#             grid2015 = KGE(grid_2015, obs),
#             grid2016 = KGE(grid_2016, obs),
#             grid2017 = KGE(grid_2017, obs),
#             grid2018 = KGE(grid_2018, obs),
#             grid2019 = KGE(grid_2019, obs),
#             grid2020 = KGE(grid_2020, obs),
#             gridall = KGE(grid_all, obs),
#             statn2011 = KGE(statn_2011, obs),
#             statn2012 = KGE(statn_2012, obs),
#             statn2013 = KGE(statn_2013, obs),
#             statn2014 = KGE(statn_2014, obs),
#             statn2015 = KGE(statn_2015, obs),
#             statn2016 = KGE(statn_2016, obs),
#             statn2017 = KGE(statn_2017, obs),
#             statn2018 = KGE(statn_2018, obs),
#             statn2019 = KGE(statn_2019, obs),
#             statn2020 = KGE(statn_2020, obs),
#             statnall = KGE(statn_all, obs)) %>%
#     mutate_if(is.numeric,
#             round,
#             digits = 2)
# 
# 
# reach_kge_all <- reach_kge_all %>%
#   pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
#   pivot_wider(names_from = 'reach', values_from = 'KGE')
# 
# 
# kable(reach_kge_all) %>%
#   kable_styling(full_width = F)
# 
# 
# obs_count <- reach_pivot %>%
#   select(obs, reach) %>%
#   drop_na() %>%
#   group_by(reach) %>%
#   summarize(count_obs = n())
# 
# kable(obs_count, caption = 'Streamflow observation count') %>%
#   kable_styling(full_width = F)

@@

>>>>

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)

@@

# plot time series of LAI over for HRU 12
{hru_select %>%
  mutate(year = year(time)) %>% 
  filter(value == 12) %>% 
ggplot(aes(x = time)) +
  geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) +
  geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) +
  ggtitle('LAI over time for HRU 12 (unburned)') +
  scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange', 
                                            "HRU12_unburn_statn"='springgreen4')) +
  theme_bw()} %>%
  ggplotly()

@@

## HRU 29 LAI and biomass

```{r hru29 lai and biomass}

# plot time series of LAI 29
hru_grid29 <- hru_grids %>%
  filter(ID == 29) %>%
  dplyr::select(time, ID, LAI_grid = LAI)

hru_statn29 <- hru_statn %>%
  filter(ID == 29) %>%
  dplyr::select(time, ID, LAI_statn = LAI)

hru_29 <- left_join(hru_grid29, hru_statn29, by = c('time', 'ID'))

# plot time series of LAI over for HRU 29
{hru_29 %>%
  ggplot(aes(x = time)) +
  geom_line(aes(y = LAI_grid, color = "HRU29_grid"), size = 1) +
  geom_line(aes(y = LAI_statn, color = 'HRU29_statn'), size = 1) +
  ggtitle('LAI - HRU 29') +
  scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange', 
                                            "HRU29_statn"='springgreen4')) +
  theme_bw()} %>%
  ggplotly()

hru29grid_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_grid.csv') %>%
  mutate(time = mdy(time)) %>%
  dplyr::select(time, BioAct_grid = BioAct_kgha)

hru29statn_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_statn.csv') %>%
  mutate(time = mdy(time)) %>%
  dplyr::select(time, BioAct_statn= BioAct_kgha)

hru_29_bio <- left_join(hru29grid_bio, hru29statn_bio, by = c('time'))

#plot time series of biomass over time for HRU 29
{hru_29_bio %>%
  ggplot(aes(x = time)) +
  geom_line(aes(y = BioAct_grid, color = "HRU29_grid"), size = 1) +
  geom_line(aes(y = BioAct_statn, color = 'HRU29_statn'), size = 1) +
  ggtitle('Biomass') +
  scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange', 
                                            "HRU29_statn"='springgreen4')) +
  theme_bw()} %>%
  ggplotly()

@@

# Mauscript figs

## Figure 1

```{r fig1}

library(usmap)

dem <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/cutDEM.tif')

hru_bnds <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')

tm_shape(dem) +
  tm_raster(palette = terrain.colors(5)) +
  tm_shape(hru_bnds) +
  tm_polygons(alpha =0, col = 'black') +
  tm_compass() +
  tm_scale_bar() +
  tm_layout(legend.outside = T,
            main.title = 'A')

dem2 <- as.data.frame(dem, xy = TRUE)

# ggplot() +
#  geom_polygon(data = hru_bnds, aes(x = x, y = y, fill = value)) +
#   geom_raster(data = dem2, aes(x = x, y = y,
#                                       fill = cutDEM)) +
#   theme_bw() +
#   coord_quickmap()

###################################################

catchment_mo_mean <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_mean = precip, tmean_mean = tmean, 
                solrad_mean = solRad, rh_mean = rhum)

catchment_mo_max <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ max(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_max = precip, tmax_max = tmean, 
                solrad_max = solRad, rh_max = rhum)

catchment_mo_min <- catchment %>%
  mutate(month = month(time)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ min(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_min = precip, tmin_min = tmean, 
                solrad_min = solRad, rh_min = rhum)

catchment_mo <- left_join(catchment_mo_mean, catchment_mo_max, 
                          by = c('month', 'site'))

catchment_mo2 <- left_join(catchment_mo, catchment_mo_min, 
                          by = c('month', 'site')) %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))

p_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = precip_min, ymax = precip_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'Precipitation (mm)') +
  ggtitle('B')

p_moplot

t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = tmin_min, ymax = tmax_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = expression("Mean temperature " ( degree~C)))+
  ggtitle('C')

t_moplot

sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_min, ymax = solrad_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'Solar Radiation (unit)') +
  ggtitle('D')

sol_moplot

rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = rh_min, ymax = rh_max, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  theme_bw() +
  labs(y = 'RH (%)', x= 'Month') +
  ggtitle('E')

rh_moplot

ggarrange(p_moplot+ rremove("x.text") +
               rremove("x.title") +
               rremove('x.ticks'),
             t_moplot+ rremove("x.text") +
               rremove("x.title")+
               rremove('x.ticks'), 
             sol_moplot + rremove("x.text") +
               rremove("x.title")+
               rremove('x.ticks'),
             rh_moplot,
          common.legend = T,
          legend = 'bottom',
             nrow = 4)
